Comment: Inferring Trade Costs from Trade Booms and Trade Busts

### 2017-09-26 Paper/Manuscript.tex
Update Manuscript.tex

\begin{abstract}
\cite{JMN2011} offer a method to measure trade costs that relies exclusively on bilateral exports and GDP statistics.
They argue that the reduction in trade costs was the main driving force of trade growth during the first globalization (1870-1913), whereas economic expansion was the main driving force during the second globalization (1950-2000).
This potentially important result is driven by the use of an \textit{ad hoc} aggregation method of bilateral trade costs to the country and global level.
What \cite{JMN2011} capture is the difference in the relative starting trade of dyads experiencing faster trade growth in the first and second globalization.
More generally, we cast doubts on the possibility to reach conclusions on aggregate costs with a method that excludes a priori changes in non-trade costs determinants of openness rates and hence can only rephrases the information contained in them.
\end{abstract}

>>>>

\begin{abstract}
\cite{JMN2011} offer a method to measure trade costs that relies exclusively on bilateral exports and GDP statistics.
They argue that the reduction in trade costs was the main driving force of trade growth during the first globalization (1870-1913), whereas economic expansion was the main driving force during the second globalization (1950-2000).
This potentially major result is driven by the use of an \textit{ad hoc} aggregation method of bilateral trade costs to the country and global level.
What \cite{JMN2011} capture is the difference in the relative starting trade of dyads experiencing faster trade growth in the first and second globalization.
More generally, we cast doubts on the possibility to reach conclusions on aggregate costs with a method that excludes a priori changes in non-trade costs determinants of openness rates and hence can only rephrases the information contained in them.
\end{abstract}
